Discrete Quantum Theories and Computing

### 2018-11-14 dissertation.tex
dissertation.lyx "2.2.1 Gleason's Theorem and the properties of the Born rule" Updating...

\todo{Make the meaning of Gleason's Theorem more clear? So that we
can explain the motivation of the question in Chapter~\ref{chap:Further-Discussion}}
A conventional quantum probability measure can be easily constructed
from a state $\rho$ according to the Born rule; conversely, this
is the only way to obtain a conventional quantum probability measure
according to Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.

>>>>

\todo{Make the meaning of Gleason's Theorem more clear? So that we
can explain the motivation of the question in Chapter~\ref{chap:Further-Discussion}.}
A conventional quantum probability measure can be easily constructed
from a state $\rho$ according to the Born rule; conversely, this
is the only way to obtain a conventional quantum probability measure
according to Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}.
